\begingroup
\setlength{\LTpre}{0pt}
\setlength{\LTpost}{0pt}
\setlength{\tabcolsep}{4pt}
\renewcommand{\arraystretch}{1.22}
\footnotesize
\begin{longtable}{>{\raggedright\arraybackslash}p{3.7cm} >{\centering\arraybackslash}p{1.3cm} >{\centering\arraybackslash}p{1.3cm} >{\centering\arraybackslash}p{1.3cm} >{\centering\arraybackslash}p{1.3cm} >{\centering\arraybackslash}p{1.3cm} >{\centering\arraybackslash}p{1.3cm}}
\caption{Λειτουργική Σύγκριση \ENG{E-Learning} \ENG{Standards}}
\label{tab:standards_functional_comparison}\\
\toprule
\textbf{Χαρακτηριστικό} & \textbf{\ENG{AICC}} & \textbf{\ENG{SCORM} 1.2} & \textbf{\ENG{SCORM} 2004} & \textbf{\ENG{xAPI}} & \textbf{\ENG{cmi5}} & \textbf{\ENG{LTI}} \\
\midrule
\endfirsthead

\caption[]{Λειτουργική Σύγκριση \ENG{E-Learning} \ENG{Standards} (συνέχεια)}\\
\toprule
\textbf{Χαρακτηριστικό} & \textbf{\ENG{AICC}} & \textbf{\ENG{SCORM} 1.2} & \textbf{\ENG{SCORM} 2004} & \textbf{\ENG{xAPI}} & \textbf{\ENG{cmi5}} & \textbf{\ENG{LTI}} \\
\midrule
\endhead

\midrule
\multicolumn{7}{r}{\footnotesize Συνεχίζεται στην επόμενη σελίδα}\\
\endfoot

\bottomrule
\endlastfoot

\multicolumn{7}{l}{\cellcolor{gray!15}\textit{Αρχιτεκτονική \& Περιβάλλον}} \\
\midrule
\ENG{Browser-based} & Όχι & Ναι & Ναι & Όχι & Όχι & Ναι \\
\ENG{Mobile} \ENG{support} & Περιορ. & Όχι & Όχι & Ναι & Ναι & Ναι \\
\ENG{Offline} \ENG{tracking} & Ναι* & Όχι & Όχι & Ναι & Ναι & Όχι \\
\ENG{Cloud-ready} & Όχι & Όχι & Όχι & Ναι & Ναι & Ναι \\
\midrule
\multicolumn{7}{l}{\cellcolor{gray!15}\textit{Δεδομένα \& Καταγραφή}} \\
\midrule
\ENG{Data} \ENG{model} & Σταθερό & Σταθερό & Σταθερό & Ευέλικτο & Περιορ. & \ENG{N/A} \\
\ENG{Extensions} & Όχι & Όχι & Περιορ. & Ναι & Ναι & Ναι \\
\ENG{Rich} \ENG{context} & Όχι & Όχι & Όχι & Ναι & Ναι & Μέτριο \\
\ENG{Historical} \ENG{data} & Περιορ. & Περιορ. & Περιορ. & Ναι & Ναι & Όχι \\
\midrule
\multicolumn{7}{l}{\cellcolor{gray!15}\textit{\ENG{Sequencing} \& \ENG{Navigation}}} \\
\midrule
\ENG{Simple} \ENG{sequencing} & Ναι & Ναι & Ναι & Όχι* & Ναι & Όχι \\
\ENG{Advanced} \ENG{seq.} & Όχι & Όχι & Ναι & Όχι* & Μέτριο & Όχι \\
\ENG{Adaptive} \ENG{paths} & Όχι & Όχι & Ναι & Όχι* & Όχι & Όχι \\
\midrule
\multicolumn{7}{l}{\cellcolor{gray!15}\textit{Διαλειτουργικότητα}} \\
\midrule
\ENG{LMS} \ENG{integration} & Πολύπλ. & Εύκολο & Μέτριο & Εύκολο & Εύκολο & Πολύ εύκολο \\
\ENG{External} \ENG{tools} & Όχι & Όχι & Όχι & Ναι & Ναι & Ναι \\
\ENG{Cross-platform} & Περιορ. & Περιορ. & Περιορ. & Ναι & Ναι & Ναι \\
\midrule
\multicolumn{7}{l}{\cellcolor{gray!15}\textit{Ασφάλεια}} \\
\midrule
\ENG{Authentication} & Βασικό & Βασικό & Βασικό & \ENG{OAuth} 2.0 & \ENG{OAuth} 2.0 & \ENG{OAuth} 2.0 \\
\ENG{Encryption} & Όχι & Όχι & Όχι & \ENG{HTTPS} & \ENG{HTTPS} & \ENG{HTTPS} \\
\ENG{Privacy} \ENG{controls} & Όχι & Όχι & Όχι & Ναι & Ναι & Ναι \\
\midrule
\multicolumn{7}{l}{\cellcolor{gray!15}\textit{Υιοθέτηση \& Υποστήριξη}} \\
\midrule
\ENG{Market} \ENG{adoption} & Χαμηλή & Υψηλή & Μέτρια & Αυξ. & Χαμηλή & Υψηλή \\
\ENG{Tool} \ENG{support} & Παλαιό & Εξαιρ. & Καλό & Καλό & Αναπτ. & Εξαιρ. \\
\ENG{Documentation} & Περιορ. & Εξαιρ. & Καλό & Εξαιρ. & Καλό & Εξαιρ. \\
\ENG{Active} \ENG{dev.} & Όχι & Όχι & Όχι & Ναι & Ναι & Ναι \\
\end{longtable}
\endgroup

